This document provides the reader with details regarding the implementation of the game application developed during a project in the course TDT4240 - Software Architecture. The game is a Tower Defense game written in Java for the Android operating system. Tower defense is a popular game type made popular as custom games in Warcraft III, and several other Real Time Strategy games.\cite{wiki:td}

In the sections to come, the implementation will be described, as well as testing and planning of the game. The report consists of six sections.
The first section will consist of design and implementation details. This section will describe a more detailed description of the various parts of the architecture and how the game was designed.

Then a User Manual will be added, describing how to use the application. This will consist of a description on how to start the game, how to build towers and use other in-game mechanics.

A test report will show which tests were done and their outcome. First the tests for functional requirements will be presented, then the tests for quality requirements through quality scenarios. 
The fifth section describes how the implementation of the game differs from the original architectural plan. it will also be explained why these changes were done, and discuss whether the changes could have been figured out earlier.

The last section of the report will consist of two parts. First a list of problems and issues with the implementation of the application. The second part will be a reflection on the project and a discussion of what could have been done differently if one were to start again from scratch.
